NFC and burnout in teachers - A replication and extension study

### 2021-10-25 Manuscript/Manuscript.Rmd
added more mediation results description

In order to replicate findings by Grass et al. [-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI = $`r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)` ($p = $`r round(fit_summ$FIT[["rmsea.pvalue"]], digits = 2)`,), suggests good fit of the proposed model throughout all indices.
standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.

>>>>

In order to replicate findings by Grass et al. [-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI = $`r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)` ($p = $`r round(fit_summ$FIT[["rmsea.pvalue"]], digits = 2)`,), suggests good fit of the proposed model throughout all indices.
standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
We could replicate a positive association of NFC and self control ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
However, we could neither replicate the effect of NFC on reappraisal ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "b1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
Instead, we found a significant indirect effect of NFC on reduced personal efficacy via self control ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
Additionally, NFC was negative associated with habitual use of suppression ($\beta = $`r round(fit_summ$PE$est[fit_summ$PE$label == "c1"], digits = 2)`, $p = $`r round(fit_summ$PE$pvalue[fit_summ$PE$label == "c1"], digits = 3)`), which was not the case in the study by Grass et al. [-@Grass2018].
